Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-05-13 paper.qmd
Update template

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
format: pdf
number-sections: true
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
# knitr:
#   opts_chunk:
#     fig.path: images/
# # # Uncomment for formatted version
  # elsevier-pdf:
  #   linestretch: 2
  #   keep-tex: true
  #   journal:
  #     name: European Transport Research Review
  #     formatting: preprint
  #     model: 3p
  #     cite-style: super
# # # #   # pdf: default

# # Uncomment the following line to produce the cover page
author:
  - name: Graham Farrell
    affiliations:
      - name: University of Leeds
        address: TBC
        orcid: TBC
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: 0000-0001-5679-6536
  - name: Steve O'Hern
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: tbc
keywords: 
  - Cycling
  - Hotspots 
  - Road Safety
  - Active Travel
  - Transport Planning
  - Near Misses
date: last-modified
---

>>>>

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
author:
  - name: Graham Farrell
    affiliations:
      - name: University of Leeds
        address: School of Law, University of Leeds, Leeds, UK
        orcid: 0000-0002-3987-8457
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: 0000-0001-5679-6536
  - name: Steve O'Hern
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: tbc
keywords: 
  - Cycling
  - Hotspots 
  - Road Safety
  - Active Travel
  - Transport Planning
  - Near Misses
date: last-modified
format:
  # pdf: default
  arxiv-pdf:
    keep-tex: true
linenumbers: true # Add (continuous) line numbers?
doublespacing: true # Double space the PDF output?
runninghead: "Preprint" # The text on the top of each page of the output
authorcols: false # Should authors be listed in a single column (default) or in multiple columns (`authorcols: true`)
---
